Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-05-02 paper/src/dis.tex
Add MJ's new paper

\subsection{Observational Evidence of Quiescence}\label{ssec:obshiz}
Our main argument in this paper is that the Milky Way underwent a brief quiescent phase induced by a starburst at $z\sim2$. In observations, a Milky Way-analogue would then be identified as a post-starburst galaxy (PSB). With abundance matching, we expect the Milky Way's total stellar mass to be $\sim2\times10^{10}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}. A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.

First, PSBs are not uncommon. \citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$, confirming previous work that PSBs are more common towards $z\sim2$ \citep[e.g.,][]{2016MNRAS.463..832W}. If these galaxies can be quickly rejuvenated, as the system studied in this work would suggest, then the total fraction of galaxies that go through a starburst-quenching phase may be higher.

\citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario. \citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B}.

>>>>

\subsection{Observational Connections: High Redshift Quenching}\label{ssec:obshiz}
Our main argument in this paper is that the Milky Way underwent a brief quiescent phase induced by a starburst at $z\sim2$. In observations, a Milky Way-analogue would then be identified as a post-starburst galaxy (PSB). With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}. A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.

First, PSBs are not uncommon. \citet{2023ApJ...953..119P} found that in massive galaxies ($M_* > 10^{10.6}\,\Msun$) the fraction of PSBs increases from $\sim2.7\%$ ($99/3655$) at $1.0 < z < 1.44$ to $\sim8\%$ ($89/1118$) at $2.16 < z < 2.5$. Later, \citet{2024arXiv240417945P} found that $\sim10\%$ of galaxies at $\sim10^{10.3}\,\Msun$ are quenched \citep[consistent with][]{2013ApJ...777...18M}, and $\sim30\%$ of their total sample is a PSB at $z\sim2$. If these galaxies can be quickly rejuvenated, as the system studied in this work would suggest, then the total fraction of galaxies that go through a starburst-quenching phase may be higher.

Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario. \citet{2023arXiv231212207A} found that at even lower masses ($<10^{9.5}\,\Msun$) Furthermore, the AGN quenching mechanism, which we believe to be responsible for the quenching in our system (Appendix~\ref{app:cause_qui}), is thought to operate at these redshifts \citep[e.g.][and references therein]{2023arXiv230805795B,2024arXiv240417945P}.
